### 2014-12-03 tex/short_2015/body.tex
new stuff

\begin{figure}[htb]
  \centering
%  \includegraphics[width=.8\linewidth]{test.jpg}
%  \vspace{-5cm}
  \input{fig2.tex}
  \caption{\label{fig:2Dheightmap}
           The rendered image (of \eg, a cube) as a height map seen from above,
           for a certain transformation.}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \framebox{\includegraphics[width=.8\linewidth]{test.jpg}}
  \caption{\label{fig:LargeSplatsOnCorners}
           The rendered image (of \eg, a cube) as a height map seen from above,
           for a certain transformation.}
\end{figure}

>>>>

\begin{figure}[htb]
  \centering
  \input{fig2.tex}
  \caption{\label{fig:2Dheightmap}
           The rendered image (of \eg, a cube) as a height map seen from above,
           for a certain transformation. \textbf{Droppe denne?}}
\end{figure}

@@

\begin{figure}[htb]
  \centering
  \subfigure[Server-rendered]{
    \includegraphics[width=.3\linewidth]{splat1.jpg}
  }
  \subfigure[$P_c M_c = P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat1.jpg}
  }
  \subfigure[$P_c M_c \neq P_s M_s$]{
    \includegraphics[width=.3\linewidth]{splat2.jpg}
  }
  \caption{\label{fig:LargeSplatsOnCorners}
           Splats for which depths are sampled on a planar region look nice on
  exactly this region, but contorted elsewhere, notice the corner of the cube.}
\end{figure}
